Covid-19 Fields Survey Data Protocol

### 2023-01-30 protocol/Background_and_methods_Jan_24.qmd
updated

@tbl-model shows the results of the logistic regression on vaccination status using socio-economic, geographical factors (by Health Region) and their interactions as predictors. The reference groups in each case were set as follow:  16 to 24 years (age group), White Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income). Socio-economic factors with statistically significant odds ratios were the age group of 65 years and over (OR=0.58), persons who identified as Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27), Latin American (OR=0.24), South Asian (OR=0.17) and Other Race/Ethnicity (a group  that included minorities not found elsewhere, OR=0.17), and those that lived in a household with an income bracket between CAD 25,000 and CAD 39,999.

Regarding the interaction of socio-economic and geographical factors, statistically significant odds ratios were the Central Health Region and Income of 15000 to 24999 CAD (OR=0.4), Age Group of 65 years and older with a household income between 25000 and 39999 CAD (OR=0.001), and with an income between 40000 and 59999 (OR=3.12)

>>>>

@tbl-model shows the results of the logistic regression on vaccination status using socio-economic, geographical factors (by Health Region) and their interactions as predictors. The reference groups in each case were set as follows:  16 to 24 years (age group), White Caucasian (Race), Toronto (Health Region), Over CAD 90,000 (Income). Socio-economic factors with statistically significant odds ratios were the age group of 65 years and over (OR=0.44), persons who identified as Arab/Middle Eastern (OR=0.15), Black (OR=0.17), Indigenous (OR=0.27), Latin American (OR=0.24), South Asian (OR=0.4) and Other Race/Ethnicity (a group  that included minorities not found elsewhere, OR=0.17), and those that lived in a household with an income bracket between CAD 25,000-39,999 (OR=0.23).

Regarding the interaction effects, the interaction of the Central Health Region and income bracket between 15000 to 24999 CAD was statistically significant (OR=0.4). In age group and income, significant effects were estimated for those 65 years and older with a household income between CAD 25000-39999 (OR=7.21), and with an income between CAD 40000-59999 (OR=3.12). In the case of race and income, significant effects were estimated for individuals that identified as Arab/Middle Easterners with a family income between 15000 and 24999 (OR=5.68) or income under CAD 15000 (OR=4.21), Black individuals with a family income under CAD 15000 (OR=4.26) or between CAD 15000-24999 (OR=3.35); additionally, there were statistically significant interaction effects in the case of those that identified as belonging to a race not identified elsewhere ("Other") within multiple income brackets: under CAD 15000 (OR=3.73), between 15000 and 24999 (OR 11.2), between 25000 and 39999 CAD (OR=4.67), and with income CAD 40000-59999 (OR=9.58). Finally, there was a significant interaction effect for South Asian individuals with an income under CAD 15000 (OR=3.10).

### 2023-01-30 protocol/Background_and_methods_Jan_24.tex
updated

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/25/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi

@@

Regarding the interaction effects, the interaction of the Central Health
Region and income bracket between 15000 to 24999 CAD was statistically
significant (OR=0.4). In the age group and income interaction effect,
significant effects were estimated for those 65 years and older with a
household income between 25000-39999 CAD (OR=0.001), and with an income
between 40000 and 59999 (OR=3.12). In the case of race and income,
significant effects were estimated for individuals that identified as
Arab/Middle Easterners with a family income between 15000 and 24000
(OR=5.68) or income under 15000 CAD (OR=4.21), Black individuals with a
family income under 15000 CAD (OR=4.26) or between 15000 and 24999 CAD
(OR=3.35); additionally, there were statistically significant
interaction effects in the case of those that identified as belonging to
a race not identified elsewhere with an income under 15000 CAD
(OR=3.73), between 15000 and 24999 (OR 11.2), between 25000 and 39999
CAD (OR=4.67), or with an income between 40000 and 59999 CAD (OR=9.58).
Finally, there was also a significant interaction effect for South Asian
individuals with an income under 15000 CAD (OR=3.10).

>>>>

\title{Covid-19 Fields Survey Data Protocol}
\author{Ariel Mundo Ortiz}
\date{1/30/23}

\begin{document}
\maketitle
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi

@@

Regarding the interaction effects, the interaction of the Central Health
Region and income bracket between 15000 to 24999 CAD was statistically
significant (OR=0.4). In age group and income, significant effects were
estimated for those 65 years and older with a household income between
25000-39999 CAD (OR=0.001), and with an income between 40000 and 59999
(OR=3.12). In the case of race and income, significant effects were
estimated for individuals that identified as Arab/Middle Easterners with
a family income between 15000 and 24000 (OR=5.68) or income under 15000
CAD (OR=4.21), Black individuals with a family income under 15000 CAD
(OR=4.26) or between 15000 and 24999 CAD (OR=3.35); additionally, there
were statistically significant interaction effects in the case of those
that identified as belonging to a race not identified elsewhere with an
income under 15000 CAD (OR=3.73), between 15000 and 24999 (OR 11.2),
between 25000 and 39999 CAD (OR=4.67), or with an income between 40000
and 59999 CAD (OR=9.58). Finally, in race and income there was a
significant interaction effect for South Asian individuals with an
income under 15000 CAD (OR=3.10).
